Visual Diagnostics for Constrained Optimisation with Application to Guided Tours

### 2021-03-27 paper/zhang-cook-laa-langrene-menendez.Rmd
Final touch done

1) the distance between the basis found and the current basis needs to be larger than 1e-3;
2) the relative change of the index value needs to be larger than 1e-5; and
3) the alpha parameter on itself needs to be larger than 0.01

@@

The holes index function used for all the examples before this section produces a smooth interpolation, while this is not the case for all the indexes An example of a noisy index function for 1D projections compares the projected data, $\mathbf{Y}_{n \times 1}$, to a randomly generated normal distribution, $\mathcal{N}_{n \times 1}$, using the Kolmogorov test. Let $F_{.}(n)$ be the ECDF function, with two possible subscripts $Y$ and $\mathcal{N}$ representing the projected and randomly generated data, and $n$ denoting the number of observation, the Normal Kolmogorov index, $I^{nk}(n)$, is defined as:

$$I^{K}(n) = \max \left[F_{Y}(n) - F_{\mathcal{N}}(n)\right]$$
With a non-smooth index function, two research questions are raised:

>>>>

1) the distance between the basis found and the current basis needs to be larger than 1e-3;
2) the relative change of the index value needs to be larger than 1e-5; and
3) the alpha parameter needs to be larger than 0.01

@@

The holes index function used for all the examples before this section produces a smooth interpolation, while this is not the case for all the indexes An example of a noisy index function for 1D projections compares the projected data, $\mathbf{Y}_{n \times 1}$, to a randomly generated normal distribution, $\mathcal{N}_{n \times 1}$, using the Kolmogorov test. Let $F_{.}(n)$ be the ECDF function (empirical cummulative distribution function), with two possible subscripts $Y$ and $\mathcal{N}$ representing the projected and randomly generated data, and $n$ denoting the number of observation, the Normal Kolmogorov index $I^{nk}(n)$, is defined as:

$$I^{K}(n) = \max \left[F_{Y}(n) - F_{\mathcal{N}}(n)\right].$$
With a non-smooth index function, two research questions are raised:

### 2021-03-27 paper/zhang-cook-laa-langrene-menendez.tex
Final touch done

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  the distance between the basis found and the current basis needs to be
  larger than 1e-3;
\item
  the relative change of the index value needs to be larger than 1e-5;
  and
\item
  the alpha parameter on itself needs to be larger than 0.01
\end{enumerate}

@@

The holes index function used for all the examples before this section
produces a smooth interpolation, while this is not the case for all the
indexes An example of a noisy index function for 1D projections compares
the projected data, \(\mathbf{Y}_{n \times 1}\), to a randomly generated
normal distribution, \(\mathcal{N}_{n \times 1}\), using the Kolmogorov
test. Let \(F_{.}(n)\) be the ECDF function, with two possible
subscripts \(Y\) and \(\mathcal{N}\) representing the projected and
randomly generated data, and \(n\) denoting the number of observation,
the Normal Kolmogorov index, \(I^{nk}(n)\), is defined as:

\[I^{K}(n) = \max \left[F_{Y}(n) - F_{\mathcal{N}}(n)\right]\] With a
non-smooth index function, two research questions are raised:

>>>>

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  the distance between the basis found and the current basis needs to be
  larger than 1e-3;
\item
  the relative change of the index value needs to be larger than 1e-5;
  and
\item
  the alpha parameter needs to be larger than 0.01
\end{enumerate}

@@

The holes index function used for all the examples before this section
produces a smooth interpolation, while this is not the case for all the
indexes An example of a noisy index function for 1D projections compares
the projected data, \(\mathbf{Y}_{n \times 1}\), to a randomly generated
normal distribution, \(\mathcal{N}_{n \times 1}\), using the Kolmogorov
test. Let \(F_{.}(n)\) be the ECDF function (empirical cummulative
distribution function), with two possible subscripts \(Y\) and
\(\mathcal{N}\) representing the projected and randomly generated data,
and \(n\) denoting the number of observation, the Normal Kolmogorov
index \(I^{nk}(n)\), is defined as:

\[I^{K}(n) = \max \left[F_{Y}(n) - F_{\mathcal{N}}(n)\right].\] With a
non-smooth index function, two research questions are raised:
